---
title: "Code Book for Getting and cleanning data project"
author: "LiangXU"
date: "Sunday, January 25, 2015"
output: html_document
---

##**Getting and Cleaning Data**

 You should create one R script called run_analysis.R that does the following. 

 - 1 Merges the training and the test sets to create one data set.

 - 2 Extracts only the measurements on the mean and standard deviation for each measurement. 

 - 3 Uses descriptive activity names to name the activities in the data set

 - 4 Appropriately labels the data set with descriptive variable names. 

 - 5 From the data set in step 4, creates a second, independent 

 tidy data set with the average of each variable for each activity and each subject.

 data from [link]https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip 
 
##**Explain the data**
train/subject_train.txt': Each row identifies the subject who performed the activity for each window sample. Its range is from 1 to 30. 
 
'features_info.txt': Shows information about the variables used on the feature vector.
 
- 'features.txt': List of all features.
 
 - 'activity_labels.txt': Links the class labels with their activity name.
 
 - 'train/X_train.txt': Training set.
 
 - 'train/y_train.txt': Training labels.
 
 - 'test/X_test.txt': Test set.
 
 - 'test/y_test.txt': Test labels.
 'train/subject_train.txt': Each row identifies the subject who performed the activity for each window sample. Its range is from 1 to 30. 
 
 - 'train/Inertial Signals/total_acc_x_train.txt': The acceleration signal from the smartphone accelerometer X axis in standard gravity units 'g'. Every row shows a 128 element vector. The same description applies for the 'total_acc_x_train.txt' and 'total_acc_z_train.txt' files for the Y and Z axis. 
 
 - 'train/Inertial Signals/body_acc_x_train.txt': The body acceleration signal obtained by subtracting the gravity from the total acceleration. 
 
 - 'train/Inertial Signals/body_gyro_x_train.txt': The angular velocity vector measured by the gyroscope for each window sample. The units are radians/second. 
 
##**Libraty Needed** 
 load the libraty needed in this project
 
```{r}
library("plyr")
library("knitr")
```
##**Init the question (read data)** 


```{r}
## download the data we need,or check the data exist or not

if(!file.exists("./data")){dir.create("./data")}
## download the file if needed
if(!file.exists("./data/Data.zip")){
fileUrl <- "https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip"
download.file(url = fileUrl,destfile = "./data/Data.zip",method = "curl")
}
##unzip the file
if(!file.exists("./data/UCI HAR Dataset")){
unzip(zipfile = "./data/Data.zip",exdir = "./data")
}
## In this project, the files in the intertial signals folders are not used. 
## so the file used here is subject,X, Y. 


## read the data from the unziped files
# from test files

File_Path_test <- "./data/UCI HAR Dataset/test"
File_Path_train <- "./data/UCI HAR Dataset/train"

test_X <- read.table(file = file.path(File_Path_test,"X_test.txt"), header = FALSE)
test_Y <- read.table(file = file.path(File_Path_test,"Y_test.txt"), header = FALSE)
test_Sub <- read.table(file = file.path(File_Path_test,"subject_test.txt"), header = FALSE)

train_X <- read.table(file = file.path(File_Path_train,"X_train.txt"), header = FALSE)
train_Y <- read.table(file = file.path(File_Path_train,"Y_train.txt"), header = FALSE)
train_Sub <- read.table(file = file.path(File_Path_train,"subject_train.txt"), header = FALSE)
data_Names <- read.table(file = file.path("./data/UCI HAR Dataset","features.txt"), header = FALSE)
#names(test_X)
```

##**1 Merges the training and the test sets to create one data set.** 

```{r}
#################################################Question 1#########################################################
# 1 Merges the training and the test sets to create one data set.
# > dim(test_X)
# [1] 2947  561
# > dim(train_X)
# # [1] 7352  561
# > datax <- rbind(test_X,train_X)
# > dim(datax)
# [1] 10299   561
Data_X <- rbind(test_X,train_X)
Data_Y <- rbind(test_Y,train_Y)
Data_Sub <- rbind(test_Sub,train_Sub)
##rename the data set X <- features Y <- Activity Sub <- Subject
names(Data_Y) <- "Activity_ID"
names(Data_Sub) <- "Subject"
names(Data_X) <- data_Names$V2
#$$$$$$$$$result<<<<<Combined Data>>>>>>>>>>>>
Data <- cbind(Data_Y,Data_Sub,Data_X)
#names(Data)
dim(Data)
```

##**2 Extracts only the measurements on the mean and standard deviation for each measurement.**
```{r}
# 2 Extracts only the measurements on the mean and standard deviation for each measurement. 
# in the name there are dffernt names
extract_features <- grepl("mean\\(\\)|std\\(\\)",data_Names$V2)
tempData <- Data[,3:563]
result2 <- tempData[,extract_features]
#$<<<<<<<<<<<<<<<<<<<<<<<<<result2 is the answer >>>>>>>>>>>>>>
str(result2)
```
##**3 Uses descriptive activity names to name the activities in the data set.**

```{r}
############################################Question 3 ################################################################
# 3 Uses descriptive activity names to name the activities in the data set
# in this part we can give more deetialed name to the data
actLabels <- read.table(file.path("./data/UCI HAR Dataset", "activity_labels.txt"),header = FALSE)
Data$Activity_ID <- factor(x = Data$Activity_ID,labels = actLabels$V2)
```

##**# 4 Appropriately labels the data set with descriptive variable names.**
```{r}
# 4 Appropriately labels the data set with descriptive variable names. 
# in this part we can give more deetialed name to the data
# t to time || Acc to accelerometer, Gyro 

names(Data)<-gsub("^t", "time_", names(Data))
names(Data)<-gsub("^f", "frequency_", names(Data))
names(Data)<-gsub("Acc", "_Accelerometer", names(Data))
names(Data)<-gsub("Gyro", "_Gyroscope_", names(Data))
names(Data)<-gsub("Mag", "_Magnitude_", names(Data))
names(Data)<-gsub("BodyBody", "_Body_", names(Data))
str(Data)
```
##**5 From the data set in step 4, creates a second, independent tidy data set with the average of each variable for each activity and each subject.**

```{r}
Clean_Data<-aggregate(. ~Subject + Activity_ID, Data, mean)
Clean_Data<-Clean_Data[order(Clean_Data$Subject,Clean_Data$Activity_ID),]
write.table(Clean_Data, file = "CleanData.txt",row.name=FALSE)
```

